---
title: "Examining the relationship between the big-5 personality facets and implicit racial attitudes"
subtitle: "Analysis"
author: "Template: Ian Hussey; content: Emilie"
date: "`2024-01-03')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

# set knit options (this way they warnings and messages will not be shown in the final document)
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

# disable scientific notation (This is set so we see the full numeric values and not an abbreviated notation)
options(scipen = 999) 

```

# Dependencies

```{r}

library(tidyverse)
library(knitr)
library(kableExtra)
library(janitor)
library(scales)

```

# Data

Load the processed data and apply the global exclusions.

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv")

#Only keep the participants flagged with 'include'. 
data_processed_after_exclusions <- data_processed |>
  filter(exclude_participant == "include")

```

# Sample descriptives

## Sample size before exclusions

```{r}

data_processed |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c( "Sample before exclusions" = 1)) |> 
  kable_classic(full_width = FALSE)

```

## Sample size after exclusions

Sample used in subsequent analyses

```{r}

data_processed_after_exclusions |>
  count(name = "n") |>
  kable() |>
  add_header_above(header = c("For analysis" = 1)) |>
  kable_classic(full_width = FALSE)

```

## Demographic Summary: Age 

Create demographics tables that summarise the mean and SD age, and the frequency and percentage of men vs women in the sample. Report the proportion of participants for which each demographics variable was available.

```{r}

data_processed_after_exclusions |>
  mutate(age = as.numeric(age)) |>
  summarise(Mean = mean(age, na.rm = TRUE),
            SD = sd(age, na.rm = TRUE)) |>
  mutate_all(.funs = janitor::round_half_up, digits = 1) |>
  kable() |>
  add_header_above(header = c("Age" = 2)) |>
  kable_classic(full_width = FALSE)


#Percentage of available data on age

library(dplyr)
library(janitor)
library(knitr)

# Assuming data_processed_after_exclusions is your dataset

 data_processed_after_exclusions |>
   filter(!is.numeric(age) & age %in% c("other/missing/error")) |>
   mutate(Percent = paste0(round_half_up((n / nrow(data_processed_after_exclusions)) * 100, 1), "%"),
          Age = stringr::str_to_sentence(age)) %>%
  kable() %>%
  kable_classic(full_width = FALSE)


```


##Demographic summary: Gender

```{r}

demographics_gender <- data_processed_after_exclusions |>
  select(gender) |>
  na.omit(T) |> 
  tabyl(gender) |>
  adorn_pct_formatting(digits = 2)

#If it is in the same format with kable: 

data_processed_after_exclusions |> 
  rename(Gender = gender) |>
  group_by(Gender) |> 
  summarise(n = n()) |> 
  mutate(Percent = paste0(round_half_up((n / sum(n)) * 100, 1), "%")) |>
  mutate(Gender = stringr::str_to_sentence(Gender)) |> # Change the case of the Gender variable so that it prints nicely
  kable() |>
  kable_classic(full_width = FALSE)

  

```


## Demographic summary: Available information 
Report the proportion of participants for which each demographics variable was available.

```{r}




```

## Gender

```{r}

data_processed_after_exclusions |> 
  rename(Gender = gender) |>
  group_by(Gender) |> 
  summarise(n = n()) |> 
  mutate(Percent = paste0(round_half_up((n / sum(n)) * 100, 1), "%")) |>
  mutate(Gender = stringr::str_to_sentence(Gender)) |> # Change the case of the Gender variable so that it prints nicely
  kable() |>
  kable_classic(full_width = FALSE)

```

# Descriptives

Descriptive statistics and plots of the measures (excluding the demographics variables)

## Self-reported evaluations

### Descriptive stats

```{r}

# overall self-reported evaluations
dat_mean_ratings <- data_processed_after_exclusions |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n()) |>
  mutate(group = "Full sample")

# self-reported evaluations by gender category
dat_mean_ratings_by_gender <- data_processed_after_exclusions |>
  group_by(group = gender) |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n())

# combine both into one table
bind_rows(dat_mean_ratings,
          dat_mean_ratings_by_gender) |>
  select(Subset = group, Mean, SD, n) |> # select variables of interest, and rename one 
  mutate(Subset = stringr::str_to_sentence(Subset)) |> # Change the case of the Subset variable so that it prints nicely
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  add_header_above(header = c(" " = 1, "Self-reported evaluations" = 3)) |>
  kable_classic(full_width = FALSE)

```

### Descriptive plot

```{r}

ggplot(data_processed_after_exclusions, aes(x = mean_evaluation)) +
  geom_histogram(binwidth = 1,
                 boundary = 0,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = viridis_pal(begin = 0.30, option = "mako")(1)) + 
  xlab("Mean self-reported evaluation") +
  ylab("Frequency") +
  theme_linedraw() +
  scale_x_continuous(breaks = pretty_breaks(n = 7)) +
  coord_cartesian(xlim = c(1, 7)) +
  theme(panel.grid.minor = element_blank())

```

## AMP evaluations

### Descriptive stats

\TODO add table of means, SDs, Ns

```{r}

### Descriptive stats

# all self evluations 

dat_mean_ratings <- data_processed_after_exclusions |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n()) |>
  mutate(group = "Full sample")

# by gender
dat_mean_ratings_by_gender <- data_processed_after_exclusions |>
  group_by(group = gender) |>
  summarise(Mean = mean(mean_evaluation, na.rm = TRUE),
            SD = sd(mean_evaluation, na.rm = TRUE),
            n = n())

# combine
bind_rows(dat_mean_ratings,
          dat_mean_ratings_by_gender) |>
  select(Subset = group, Mean, SD, n) |> 
  mutate(Subset = stringr::str_to_sentence(Subset)) |> 
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  add_header_above(header = c(" " = 1, "AMP Evaluations" = 3)) |>
  kable_classic(full_width = FALSE)

```

### Descriptive plots

```{r}

ggplot(data_processed_after_exclusions, aes(x = AMP_score)) +
  geom_histogram(binwidth = 0.05,
                 boundary = 0,
                 fill = viridis_pal(begin = 0.45, option = "mako")(1), 
                 color = viridis_pal(begin = 0.30, option = "mako")(1)) + 
  xlab("AMP score") +
  ylab("Frequency") +
  theme_linedraw() +
  scale_x_continuous(breaks = pretty_breaks(n = 10))



```

# Analyses & hypothesis tests

## Self-reported evaluations are correlated with evaluations on the AMP

### Plot

```{r}

ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.45, option = "mako")(1)) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

ggplot(data_processed_after_exclusions, 
       aes(y = AMP_score,
           x = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  geom_smooth(method = "lm",
              color = viridis_pal(begin = 0.45, option = "mako")(1)) +
  ylab("AMP score") +
  xlab("Mean self-reported evaluation") +
  theme_linedraw() 

ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

```

More complex plots:

#### Axial hisograms

Scatter plots with axial histograms using ggExtra: https://cran.r-project.org/web/packages/ggExtra/vignettes/ggExtra.html

\TODO add axial histograms to a scatter plot. In a single plot, present different regression lines split by gender, and separate axial histograms for each gender.

```{r}
library("ggExtra")
library("ggplot2")


#creating a plot 
plot1 <- ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1),
              alpha = 0.5) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw() 

ggMarginal(plot1, type = "histogram")


#Split them by gender and add regression line 

Axial_histogram_gender <- ggplot(data_processed_after_exclusions, 
                                  aes(x = AMP_score,
                                      y = mean_evaluation, 
                                      colour = gender)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "pink") +  # Add regression line
  scale_colour_discrete(name = "gender",
                        labels = c("female", "male", "non-binary")) +
  theme(legend.position = c(.15, .7))

ggMarginal(Axial_histogram_gender, type = "histogram", groupColour = TRUE, groupFill = TRUE)


#The regression line kinda shows a negative trend --> important to observe a first trend 

```

#### Labelled points

Label points using ggrepel: https://cran.r-project.org/web/packages/ggrepel/vignettes/ggrepel.html

\TODO Label the points in a scatter plot using their participant codes. Label only the participants with more extreme scores.

To change colors use:

```{r eval=FALSE, include=FALSE}
##colors 
colors <- viridis_pal(begin = 0.0, end = 1.0, option = "mako")(10)
colors
show_col(colors)
```


```{r}
library(ggrepel)
```


```{r}

#Plot 
Point_labels <- ggplot(data_processed_after_exclusions, 
       aes(x = AMP_score,
           y = mean_evaluation, 
           label = subject)) +
  geom_point (color = "red") +
  scale_colour_discrete(name = "gender",
                        labels = c("female", "male", "non-binary"))

set.seed(42)

p1 <- Point_labels + geom_text() + labs(title = "geom_text()")

p2 <- Point_labels + geom_text_repel() + labs(title = "geom_text_repel()")

gridExtra::grid.arrange(p1, p2, ncol = 2)

#R itself gives us a warning, that there are unlabeled data points and too many overlaps, so this plot is not really useful 
#a way this plot is often used is to show the outliers or identify them, this is easily done by just putting the outlier variable or an order reporting the outliers directly in to the ggplot 


```

#### Magnify areas

Magnify areas of your plot with ggmagnify: https://hughjonesd.github.io/ggmagnify/

\TODO Magnify an area of one of your scatter plots, eg where there are a lot of data points in a small area.

```{r}
# Load necessary libraries
library(ggplot2)
library(ggmagnify)

# Your original scatter plot
ggp <- ggplot(data_processed_after_exclusions, aes(x = AMP_score, y = mean_evaluation)) +
  geom_jitter(color = viridis_pal(begin = 0.45, option = "mako")(1), alpha = 0.5) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_linedraw()

# Define the area to be magnified
# Adjust these values to the area you want to zoom in on
from <- c(xmin = 0.3, xmax = 0.8, ymin = 0.8, ymax = 1.3)

# Define where to place the magnified inset on the plot
# Adjust these values to place the inset where you like
to <- c(xmin = 0, xmax = 0.25, ymin = 4, ymax = 5)

# Add the magnified area to the plot
ggp + geom_magnify(from = from, to = to)
```
### Test

\TODO run an appropriate test. Below the output, interpret the results: write a few sentences that report and interpret the results following APA reporting style.
Statistical inference test ---> Test stats and p value 
Hypothesis: Self-reported evaluations are correlated with evaluations on the AMP

```{r}

# In order tot check whether self report evaluations are correlated with the amp evaluations we remember the regression line above where we saw a slight negative trend We should test this statistically 
result <- cor.test(data_processed_after_exclusions$mean_evaluation, data_processed_after_exclusions$AMP_score, method = "pearson")

# Print the test statistics and p-value
print(result)
#if we want the results specifically
 result$p.value
 result$estimate

#we see a negative correlation however it is not significant (p = .2435), also seen in confidence interval that includes 0 suggesting that there is no correlation in the data 

# we can alos check for a spearman correlation test
 result2 <- cor.test(data_processed_after_exclusions$mean_evaluation, data_processed_after_exclusions$AMP_score, method = "spearman")

 result2$p.value
 result2$estimate

 
#for the spearman it is almost identical (not surprisingly)

```

## Self-reported evalautions differ between men and women

### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

```{r}
#####split histogram

#I included a legend in all three plots, this is not particularly useful since there are automatically created axial labels and it is looking rather overplottet, it is just for exercise reasons to see how a Legend can be included and modified (see in Chunk below)

library(ggplot2)
library(hrbrthemes)  #really cool package for better themes 

# I choose the theme ipsum (very clean there is a lot of different ones)
theme_set(theme_ipsum())

# Plotting
splithistogram <- ggplot(data_processed_after_exclusions, aes(x = mean_evaluation, fill = gender)) +
  geom_histogram(position = "dodge", binwidth = 0.5, color = "white", alpha = 0.8, size = 0.2) +
  geom_vline(xintercept = seq(0, 6, by = 6), color = "black", size = 1) + #put in lines in order to  distinguish the plots if you don't they are all kinda squished together 
  facet_wrap(~ gender, scales = "free_x") +
  xlab("Mean Evaluation") +
  ylab("Frequency of Evaluation") +
  labs(title = "Distribution of Mean Evaluation by Gender") +
  scale_fill_manual(values = c("female" = "#FF9999", "male" = "#66B2FF", "nonbinary" = "#99FF99"), guide = FALSE) + #sometimes this does not work (--> if it does not set to NONE)
  theme_minimal() +
  theme(#This is for te legend bars (really practical for some things)
    legend.position = "top",
    legend.background = element_rect(fill = "white"),
    strip.background = element_rect(fill = "lightgray", color = "white"),
    strip.text = element_text(color = "black", size = 11),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 12, face = "bold"),
    plot.title = element_text(size = 14, face = "bold"),
    panel.spacing = unit(0.0, "lines")  #Here we can reduce the space between the bars 
  ) +
  theme(
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 12, face = "bold"),
    plot.title = element_text(size = 14, face = "bold")
  ) +
  scale_x_continuous(expand = c(0.05, 0.05)) + # Adjust the space on the x axis (both ends)
  coord_cartesian(xlim = c(0, 6))  # Since we have a scale from 1-6 we can fix the scale for all to show from 1-6 in order to see the distribution
# Print the plot
print(splithistogram)

  
#With regard to the hypothesis we see a differing distribution which could lead to a significant hypothesis (men and women differing in their self reports)


##### Violin Plot 
#Theme 
theme_set(theme_ipsum_ps()) # choosing a different theme this time in order to experiment a bit

# Violin Plot
splitviolin <- ggplot(data_processed_after_exclusions, aes(x = gender, y = mean_evaluation, fill = gender)) +
  geom_violin(scale = "width", trim = FALSE, alpha = 0.7, color = "black") +
  geom_boxplot(width = 0.1, fill = "white", color = "black", alpha = 0.7) +
  xlab("Gender") +
  ylab("Mean Evaluation") +
  theme_minimal() +
  theme(
    legend.position = "top", #we put top instead of a vector since it is not pretty with the vector (see above how to do with a vector)
    legend.background = element_rect(fill = "white"),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 16, face = "bold"),
    panel.spacing = unit(0.0, "lines")) +
  scale_fill_manual(values = c("female" = "#FF9999", "male" = "#66B2FF", "nonbinary" = "#99FF99")) +
  coord_cartesian(ylim = c(0, 6))

# Print 
print(splitviolin)

#The violin plot offers a bit more information on the distribution of the self evaluations. Since there are so little people having a nonbinary gender the wide distribution is not surprising. Whereas for men and women there is more to interpret --> The median is different and women have a less higher distribution also suggesting that the two genders might differ. 


#####raincloud plot
library(ggplot2)
library(ggdist)#used for flat violin
library(hrbrthemes)


# Set the theme
theme_set(theme_ipsum())


raincloudplot <- ggplot(data_processed_after_exclusions, aes(x = gender, y = mean_evaluation, fill = gender)) +
  geom_violin(scale = "width", trim = FALSE, alpha = 0.5, color = "black") +
  geom_point(aes(color = gender), position = position_jitter(width = 0.1), size = 2, alpha = 0.5) +
  geom_boxplot(width = 0.1, fill = "white", color = "black", alpha = 0.7) +
  labs(x = "Gender", y = "Mean Evaluation") +
  theme_minimal() +
  theme(
    legend.position = "top",  # Adjust legend position to the top
    legend.background = element_rect(fill = "white"),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 12, face = "bold"),
    plot.title = element_text(size = 14, face = "bold"))



# Print the plot
print(raincloudplot)


#The raincloud plot suggests the same as above with women having some outliers where men still have distribution in violin plot. The overall plotting suggests that the hypothesis is supported. 



```

### Test

\TODO run an appropriate test. Below the output, interpret the results: write a few sentences that report and interpret the results following APA reporting style.


Self-reported evalautions differ between men and women 

```{r}
#T-Test to check for possible differences 

#Create one dataset for male and female 
data_male <- subset(data_processed_after_exclusions, gender == "male")
data_female <- subset(data_processed_after_exclusions, gender == "female")


#doing a T-Test with the mean_evaluation self reports 
t_test_result <- t.test(mean_evaluation ~ gender, data = rbind(data_male, data_female))

#Printing the results in order to see whether it is significant or not: 
print(t_test_result)


library(report)
report_table(t_test_result)
report_effectsize(t_test_result)
report_text(t_test_result)



#If a T-Test is not possible (this is the case when there is more than two independent groups) we can conduct a Kruskal_Wallis-Test. If we would like to include all genders (not only men and women), a Kruskal test is appropriate. 

kruskal_result <- kruskal.test(mean_evaluation ~ gender, data = data_processed_after_exclusions)

# Print the result
print(kruskal_result)

#Similarly, the Kruskal-Wallis test confirms the previously indicated significance. Likewise the p-value is clearly below 0.5 (p= 0.0037) and thus indicates a significant difference with regard to the self-reported average evaluation in men, women and non-binary individuals. 

```

## Evaluations on the Affect Misattribution Procedure differ between men and women

### Plot

\TODO split histogram, split violin plot, raincloud plot, etc.

This time, vary the labeling and order of the legend, e.g., capitalise "Men" and "Women", and know how to change the order of the factors.

```{r}
#####Split Histogram 
#vary the labeling and order of the legend 
# We can define custom labels and vary their order so the legend shows different things 
custom_labels <- c( "Women", "Non-binary", "Men") # here we can vary the names and order within the legend 
custom_order <- c("female", "nonbinary", "male" ) #with this we can adjust the custom order

#ATTENTION: The order of the custom labels and order has to be the same otherwhise the legend and the order is not matched 

#In order to be able to reorder them we have to change the factor since otherwhise there is absolutely nothing happening 
data_processed_after_exclusions$gender <- factor(data_processed_after_exclusions$gender, 
                                                 levels = custom_order)

#we can then easily insert them into our splithistogram like that 
splithistogram2 <- ggplot(data_processed_after_exclusions, aes(x = AMP_score, fill = gender)) +
  geom_histogram(position = "dodge", binwidth = 0.15, color = "black", alpha = 0.7) +
  facet_grid(. ~ gender) +
  xlab("AMP score") +
  ylab("Mean self-reported evaluation") +
  theme_minimal() +
  theme(legend.position = c(0.51, 0.8), legend.background = element_rect(fill = "white")) +
  scale_fill_manual(values = c("female" = "red", "male" = "blue", "nonbinary" = "green"),  
                    labels = custom_labels) +
  labs(fill = "Gender")  # We could also capitalize the header (title) of the legend


# Print the plot
print(splithistogram2)

#As we can see the legend is changed now with all things being capitalized --> in order to change them again we can adjust the vector 



#####Split violin plot 
#change the order of the violin plot (same as above) --> it is the same custom labels and order if we would like different ones we would have to name them differently in order to not get things mixed up 
custom_labels <- c( "Women", "Non-binary", "Men") 
custom_order <- c("female", "nonbinary", "male" )

# Reorder the level
data_processed_after_exclusions$gender <- factor(data_processed_after_exclusions$gender, 
                                                 levels = custom_order)

# Split violin with the legend being modified 
splitviolin2 <- ggplot(data_processed_after_exclusions, aes(x = gender, y = AMP_score, fill = gender)) +
  geom_violin(scale = "width", trim = FALSE, alpha = 0.7, color = "black") +
  geom_boxplot(width = 0.1, fill = "white", color = "black", alpha = 0.7) +
  facet_wrap(~gender, scales = "free_x") +
  xlab("Gender") +
  ylab("AMP Score") +
  theme_minimal() +
  theme(legend.position = c(0.5, 0.2), legend.background = element_rect(fill = "white")) +
  scale_fill_manual(values = c("female" = "red", "male" = "blue", "nonbinary" = "green"),  
                    labels = custom_labels,
                    breaks = custom_order)

# Print the plot
print(splitviolin2)



##### Raincloud plot
library(ggbeeswarm)

#We are again taking our same labels as above ( we do not have to read them in all of the time but it is better to have an intersubjective view of what happened)
custom_labels <- c( "Women", "Non-binary", "Men") 
custom_order <- c("female", "nonbinary", "male" )

#reorder the levels (again same thing as previously done)
data_processed_after_exclusions$gender <- factor(data_processed_after_exclusions$gender, 
                                                 levels = custom_order)


#Create the plot 
raincloudplot2 <- ggplot(data_processed_after_exclusions, aes(x = gender, y = AMP_score, fill = gender)) +
  geom_violin(trim = FALSE, scale = "area", adjust = 1.5, alpha = 0.5) +
  geom_boxplot(width = 0.1, outlier.shape = NA, alpha = 0.5) +
  geom_quasirandom(aes(color = gender, fill = gender), size = 2, alpha = 0.5, show.legend = FALSE) +
  scale_x_discrete(labels = custom_labels) + #Changing the labels of the automatically created axial labels to the one we have customed. 
  scale_color_manual(values = c("female" = "red", "male" = "blue", "nonbinary" = "green"),  #we adjust the colours because otherwise the points and plots do not match
                    labels = custom_labels,
                    breaks = custom_order) +
  scale_fill_manual(values = c("female" = "red", "male" = "blue", "nonbinary" = "green"),  
                    labels = custom_labels,
                    breaks = custom_order) +
  labs(x = "Gender", y = "AMP Score") +
  theme_minimal() +
  theme(legend.position = c(0.51, 0.2), legend.background = element_rect(fill = "white"))


# Print the plot
print(raincloudplot2)

```

### Test
Hypothesis from above: Evaluations on the Affect Misattribution Procedure differ between men and women

\TODO run an appropriate test. Below the output, print an interpretation of the results generated by the 'easystats' package [report](https://easystats.github.io/report/). I.e., use `report::report()`.

```{r}

#t test


data_tests <- rbind(data_male, data_female)


AMP_t_test_result <- t.test(AMP_score ~ gender, data = data_tests)
print(AMP_t_test_result)


report_table(AMP_t_test_result)
report_effectsize(AMP_t_test_result)

report_text(AMP_t_test_result)

```

## Combining plots

Combine plots using the library [patchwork](https://patchwork.data-imaginist.com/).

\TODO Combine at least three of the above plots into one.

```{r}

#The put together plots don't really make any sense since they do not have the same labels on the axis, yet it is an example of how it should work. In order to remove the automatically created axial labels we could change this directly within the plots themselves 
# you can combine things with patchwork
library(patchwork)


#First we have to remove the legends from the plots 

splithistogram2_plot <- splithistogram2_plot + theme(legend.position = "none") 
splitviolin2_plot <- splitviolin2 + theme(legend.position = "none") 
raincloudplot2_plot <- raincloudplot2 + theme(legend.position = "none") 

#Combining a plot (with +)
combined_plot <- splithistogram2_plot + splitviolin2_plot + raincloudplot2_plot


print(combined_plot)

#This does not look too pretty so you can modify the codes 


# Customize the appearance of the combined plot
combined_plot <- (splithistogram2_plot + splitviolin2_plot + raincloudplot2_plot +
  plot_layout(ncol = 3) +  # Set the number of columns
  theme_minimal() +        # Use a minimal theme
  theme(
    plot.margin = margin(15, 15, 15, 15),  # Adjust overall margins
    strip.text = element_text(size = 10),   # Adjust text size in facet labels
    legend.position = "bottom",             # Move the legend to the bottom
    legend.direction = "horizontal",        # Arrange legend items horizontally
    legend.box = "horizontal" , 
  axis.text.x = element_blank(),          # Remove x-axis labels
    axis.text.y = element_blank() # Use a horizontal legend box
  )
)

# Print the customized combined plot
print(combined_plot)


```

TODO: Calculate Cronbachs Alpha for like, positive, prefer 

```{r}

library(psych)



alpha(subset(data_processed_after_exclusions, select = c(like, positive, prefer)), check.keys = T)#check keys just does change the inverted items (we do not have them)

#cronbachs Alpha is 0.877 





```



## Saving plots

Save plots to disk with `ggsave()`

\TODO Save the above combined plot to disk as both .png and .pdf. Ensure the png has at least 300dpi resolution.

```{r}

ggsave("combined_plot.png", combined_plot, width = 15, height = 5, units = "in", dpi = 300)

ggsave("combined_plot.pdf", combined_plot, width = 15, height = 5, units = "in", dpi = 300)

#Both of them are in the same folder as analysis and processing


```

# Session info

```{r}

sessionInfo()

```



